humanCdGF_disease_severity

### 2017-02-01 code/CdGF_disease_severity.Rmd

---
title: "humanCdGF_disease_severity"
author: "Nicholas Lesniak"
date: "October 27, 2016"
output: html_document
---

@@

```{r setup, include=FALSE}
meta_file   <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF_metadata.txt'
shared_file <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF.an.unique_list.0.03.subsample.shared'
tax_file <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/mothur/gf_all.an.cons.taxonomy'
tax_function <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/code/tax_level.R'

@@

# Weight loss  
meta_file %>% 
  filter(day %in% c(0:10), !is.na(percent_weightLoss) ) %>%
  filter(!cage_id == 'NP1') %>% 
  select(mouse_id, day, Early_Euth, percent_weightLoss, cage_id) %>% 
  ggplot(aes(x = factor(day), y = percent_weightLoss, color = factor(Early_Euth))) + 
        geom_jitter(width = 0.5, alpha = 0.1) + 
        scale_color_manual(values = c('black', 'red'), breaks=c("FALSE", "TRUE"),
                           labels=c("Persistent", "Severe")) +
        stat_summary(fun.y=median, geom="line", aes(group = Early_Euth)) +
        labs(x = 'Day', y = ' Percent Relative to Day 0', title = 'Weight Loss') +
        theme(legend.justification=c(1,0), legend.position=c(1,0.1), 
                  legend.title=element_blank()) +
          stat_summary(fun.data = 'median_hilow')

# C. Diff CFU
meta_file %>% 
  filter(day %in% c(0:10), !is.na(log_cfu) ) %>%
  filter(!cage_id == 'NP1') %>% 
  select(mouse_id, day, Early_Euth, log_cfu, cage_id) %>% 
  ggplot(aes(x = factor(day), y = log_cfu, color = factor(Early_Euth))) + 
        geom_jitter(width = 0.5, alpha = 0.2) + 
        scale_color_manual(values = c('black', 'red'), breaks=c("FALSE", "TRUE"),
                           labels=c("Persistent", "Severe")) +
        stat_summary(fun.y=median, geom="line", aes(group = Early_Euth)) +
        labs(x = 'Day', y = ' CFU (log10)', title = 'C. Difficile Colonization') +
        theme(legend.justification=c(1,0), legend.position=c(1,0.2), 
                  legend.title=element_blank()) +
        stat_summary(fun.data = 'median_hilow')
```

>>>>

---
title: "humanCdGF_disease_severity"
author: "Nicholas Lesniak"
date: "January 11, 2017"
output: html_document
---

@@

```{r process data, include=FALSE}
meta_file   <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF_metadata.txt'
shared_file <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF.an.unique_list.0.03.subsample.shared'
tax_file <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/gf_new.an.taxonomy'
tax_function <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/code/tax_level.R'

@@

# Weight loss  
meta_file %>% 
  filter(day %in% c(0:10), !is.na(percent_weightLoss) ) %>%
  filter(!cage_id == 'NP1') %>% 
  select(mouse_id, day, Early_Euth, percent_weightLoss, cage_id) %>% 
  ggplot(aes(x = factor(day), y = percent_weightLoss, color = factor(Early_Euth))) + 
        geom_jitter(width = 0.3, alpha = 0.1) + 
        scale_color_manual(values = c('black', 'red'), breaks=c("FALSE", "TRUE"),
                           labels=c("Persistent", "Severe")) +
        stat_summary(fun.y=median, geom="line", aes(group = Early_Euth)) +
        labs(x = 'Day', y = ' Percent Relative to Day 0', title = 'Weight Loss') +
          stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5)) +
        theme_bw() +
        theme(legend.justification=c(1,0), legend.position=c(1,0.1), 
              legend.title=element_blank())

# C. Diff CFU
meta_file %>% 
  filter(day %in% c(0:10), !is.na(log_cfu) ) %>%
  filter(!cage_id == 'NP1') %>% 
  select(mouse_id, day, Early_Euth, log_cfu, cage_id) %>% 
  ggplot(aes(x = factor(day), y = log_cfu, color = factor(Early_Euth))) + 
        geom_jitter(width = 0.3, alpha = 0.2) + 
        scale_color_manual(values = c('black', 'red'), breaks=c("FALSE", "TRUE"),
                           labels=c("Persistent", "Severe")) +
        stat_summary(fun.y=median, geom="line", aes(group = Early_Euth)) +
        labs(x = 'Day', y = ' CFU (log10)', title = 'C. Difficile Colonization') +
        theme(legend.justification=c(1,0), legend.position=c(1,0.2), 
                  legend.title=element_blank()) +
        stat_summary(fun.data = 'median_hilow', fun.args = (conf.int=0.5)) + 
        theme_bw() +
        theme(legend.justification=c(1,0), legend.position=c(1,0.2), 
              legend.title=element_blank())

```

Points are median of Disease Severity Group and lines are IQR
